%----------------------------------------------------------------------------------------
%	Paquetes y otras configuraciones
%----------------------------------------------------------------------------------------

\documentclass[margin]{res}
\title{cv_en}
\usepackage{helvet}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\setlength{\textwidth}{5.1in}

\begin{document}

%------------------------------
%	Nombre y dirección
%------------------------------
\moveleft.5 \hoffset \centerline{\LARGE \bf Ian Castillo}
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 
% \moveleft.5\hoffset\centerline{Genero: Masculino | Edad: 23 años}
\moveleft.5\hoffset\centerline{iancastillorosales@gmail.com | \faTwitter: ian\_castill0}
% \moveleft.5\hoffset\centerline{github: carian2996 \hspace{0.2cm} linkedin: iancr}
% \moveleft.5\hoffset\centerline{Mexico City, Mexico}
% \moveleft.5\hoffset\centerline{Móvil: +52 55 2132 5415}

%------------------------------

\begin{resume}

%------------------------------
%	Objetivo
%------------------------------
\section{SUMMARY}
 With more than 5 year of experience in \textit{Data Science}, I create actionable knowledge from data to be leveraged in decision making and product development. My areas of expertise are Data Analytics, Experimentation and Machine Learning.

%------------------------------
%	Experiencia profesional
%------------------------------
\section{EXPERIENCE} 
\textbf{Data Scientist @ Uber} \hfill 2017 -- Current \\
As part of the \textit{LatAm Data Science} team I contribute with advance Analytics to design Uber's strategy guiding the company to achieve its goal. I collaborated in different projects such as:  \\
\begin{itemize}
    \item \textbf{Loyalty Program}: I worked with regional and international teams to design experiments, coordinating data engineer requirements and insights generation to later recommend actions and provide evidence resulting in the expansion of the Loyalty program over 10+ countries reaching +1M drivers at LatAm.
    \item \textbf{Customer Segmentation}: I led efforts to translate the customer behaviour that was captured with a manual process taking up to 8 hours by week to a fully automated a data workflow (including data pre-processing, exploration and modeling) handling over dozen of millions of transactions within hours. This accomplishment allow the business to take decisions based on the customer's behaviour with Uber's products.
\end{itemize}

\textbf{Data Analyst @ Uber Eats} \hfill 2017 -- 2018 \\
I built the ground to achieve an analytical efficiency to create strategies and policies giving the best support experience for users. I was responsible to develop and monitor key operational indicators to deliver stakeholders meaningful insights.
% \textbf{Achievement}: Improved stakeholders visibility from taking actions on a weekly basis to have root causes understanding based on information to generate strategies in a long term.


\textbf{Data Scientist @ Conlana} \hfill 2016 -- 2017 \\
% \textbf{Data Scientist} \\
Conlana was a micro-leading startup company targeting low-income population. I led a BI team (2 members) to build data tools and predictive models that improved the business operations. 
% During the emerging Fintech environment in Mexico, I worked as data scientist building analytical models to reach a different offer. Our team started building the core element in the start-up: the risk model. After we gained enough traction and growth 

% \textbf{Grupo Salinas: Business Intelligence Group} \hfill 2015 -- 2016 \\
% With a recently created team, the BI group was aimed to understand how a financial environment worked with a dozen of products belonging to the same corporation. I participated in multiple projects with the objective of analyze relationships between banking (personal credit and collection) to other services (from telcom to retail).
% Meaningful insights from data helped to provide decision makers with intelligence. Becoming a business owner and leveraging data analysis and I contributed to help my team become one of the first advanced analytical teams within the company. My role as data analyst allowed me introduced myself in the Data Science path.

%------------------------------
%	Education
%------------------------------
\section{EDUCATION} 
{\sl Junior Research Fellow} \hfill 2014 -- 2015 \\
\textbf{CIMAT, Mathematics Research Center} \\
Scholarship granted for thesis elaboration on probabilistic models known as Optimal Stopping Problems, which determine the best moment to make a decision and react to a sequence of observations that come from a stochastic process, trying to maximize the expected gains or minimize expected costs.

{\sl Diploma in Big Data as Business Strategy} \hfill 2015 -- 2016 \\
\textbf{ITESM - Tecnologico de Monterrey}. \\
I acquired valuable knowledge on how data analysis over large data sets can have an impact during different phases of a business. During this specialization I managed different tools in the Big Data environment, in particular, data storage, processing and transforming information, machine learning at scale.

\pagebreak

{\sl BSc in Mathematics (Minor in Probability)} \hfill 2010 -- 2014 \\
\textbf{Universidad Nacional Autonoma de México}. \\
I am specialist in detection, control and prediction of risk through mathematical models. Two years of mathematics: Calculus, Algebra, Geometry, Probability and Statistics, plus two years based on Advanced Probability and Statistics courses.
% The core of my knowledge. Two years of elemental Mathematics studies: Calculus, Algebra, Geometry, Probability and Statistics plus two years of Probability and Statistics Advanced courses combined with an self-taught computational study. I am specialist in the recognition, control and prediction of risk through detection of patterns in data.  % Promedio 8.6. En proceso de titulación.
% Promedio 8.6

%------------------------------
%   SKILLS
%------------------------------

\section{TOP SKILLS} 
\begin{tabular}{ l l }

%------------------------------
%	HABILIDADES EN CIENCIA DE DATOS
%------------------------------
\textbf{Hard core} \\
Data Modeling    & Presto/Hive, Airflow\\ 
Data Analysis    & Python, pandas, numpy \\ 
Experimentation  & scipy, matplotlib \\ 
Machine Learning & scikit-learn, PySpark \\ 
\\

%------------------------------
%	HABILIDADES DE NEGOCIO
%------------------------------
\textbf{Soft core} \\
Business Acumen & Teamwork \\
Communication   & Stakeholder Management \\

\end{tabular}
%------------------------------
%	Idiomas
%------------------------------
\section{LANGUAGES}
\begin{tabular}{ l l }
  Spanish & \hspace{1.6cm} Native \\
  English & \hspace{1.6cm} Advance \\
  % & \hspace{1.6cm} TOEFL 92 (R22, L25, S23, W22) \\
  % Portuguese & \hspace{1.6cm} Basic
\end{tabular}

%------------------------------
%	Otros cursos
%------------------------------
\section{COURSES}

% {\sl Specialization in Machine Learning (MOOC)} \\
% \textbf{University of Washington}, through Coursera. (08/2016 -- Present)

% {\sl Data Structures and Algorithms Specialization (MOOC)} \\
% \textbf{University of California, San Diego}, through Coursera. (01/2017 -- Present)

% {\sl Methods and Statistics in Social Sciences (MOOC)} \\
% \textbf{University of Amsterdam, Netherlands}, through Coursera. (04/16 -- Present)

{\textbf{Big Data Specialization} \\
University of California, San Diego, through Coursera. (2015) \\
(MOOC, License: KZHPE3BE53T9)}

{\textbf{Specialization: Python for Everybody} \\
University of Michigan, through Coursera. (2015) \\
(MOOC, License: WS7AFG7ADL45)}

{\textbf{Data Science Specialization} \\
Johns Hopkins University, Maryland, through Coursera. (2014) \\
(MOOC, License: SR5SCBLSE3JR)}

%------------------------------
%	Actividades extracurriculares
%------------------------------
% \newpage
\section{OTHER \\ ACTIVITIES} 
% {\sl Un-Student} \hfill 2014 \\
% \textbf{Dev.f Hacker School}. \\
% Attendant to summer school Dev.f, aimed to develop mental skills, team work and solutions for social problems. I worked with a multidisciplinary team to propose a solution to encourage money saving culture in young people with the use of technology.

{\sl Internship} \hfill 2014 \\
\textbf{Central Bank of Mexico}. \\
I participated in the Central Bank of Mexico internship program doing data analysis in the Department of Foreign Currencies and Derivatives where I migrated multiple statistical processes written in SPSS to the R language, likewise I supported the team with statistical analysis and data visualizations.

% {\sl Assistant} \hfill 07/2013 \\
% \textbf{Latin American School and Symposium of Bayesian Statistics}. \\
% Assistant to First Latin American School and Symposium of Bayesian Statistics, San José, Costa Rica.

{\sl Assistant Lecturer} \hfill 2013 \\
\textbf{Calculus / Linear Algebra}. \\
Teaching Introductory concepts of Calculus and Algebra. Helped professors with duties in class and creating class materials: notebooks, tests, presentation and academic research.

% %------------------------------
% %   RECONOCIMIENTOS
% %------------------------------
% \section{ACHIE \\ VEMENTS} 
% \textbf{Coursera's Top Learner: Mexico City.} {\sl Invited by Stéphanie Durand to offer feedback on Coursera Platform Latin America.}

% %------------------------------
% %   RECONOCIMIENTOS
% %------------------------------
% \section{VOLUNTEER} 
% \textbf{Coursera's Global Translator.} {\sl Volunteer translator in Coursera's platform.} \\
% \textbf{Moovit's Volunteer.} {\sl Volunteer mapping public transportation routes in Mexico City.}

\end{resume}
\end{document}